Web Processing - Standardised GIS Analyses for Cable Route Planning

### 2022-11-25 paper/paper-CableRoute.tex
update and bug fixes for rules2weights.py:  -  added parallel processing for buffering larger files  - bug fix apply filtering by bbox after reprojection
requirements.txt:
 - add ray for multiprocessing

paper-CableRoute.tex
 - add bibtex
 - changed document class
 - add chapters
 -  add first text for chapter `Methods`

\documentclass[acmsmall]{acmart}

@@

@@

	\author{Sebastian Heiden}
	\email{u38XXX@hs-harz.de}
	\affiliation{%
		\institution{Harz University of Applied Sciences}
		\streetaddress{Friedrichstrasse 57-59}
		\city{Wernigerode}
		\state{Saxony-Anhalt}
		\country{Germany}
		\postcode{38855}
	}

@@

	\section{Template Overview}

	\subsection{Template Styles}

	\subsection{Template Parameters}

	\section{Modifications}

	\section{Typefaces}

	\section{Title Information}

	\section{Authors and Affiliations}

	\section{Rights Information}

	\section{CCS Concepts and User-Defined Keywords}

	\section{Sectioning Commands}

	\section{Tables}

	\section{Math Equations}

	\subsection{Inline (In-text) Equations}

	\subsection{Display Equations}

	\section{Figures}

	\section{Citations and Bibliographies}

	\section{Acknowledgments}

\section{Multi-language papers}

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

>>>>

% !TeX spellcheck = en_US

\documentclass[acmtog]{acmart}
\usepackage[acronym]{glossaries}

@@

\newacronym{wfs}{wfs}{Web Feature Service}

@@

	\author{Sebastian Heiden}
	\email{u38439@hs-harz.de}
	\affiliation{%
		\institution{Harz University of Applied Sciences}
		\streetaddress{Friedrichstrasse 57-59}
		\city{Wernigerode}
		\state{Saxony-Anhalt}
		\country{Germany}
		\postcode{38855}
	}

@@

	\section{Methods}
	We retrieve a set of different spacial data-sets from  public sources as a basis to create the cost raster. Field of study are the counties of Cuxhaven and Osterholz in the state of Lower Saxony, Germany.
	Areas protected by different European and National conservation laws are provided by the German Environment Agency as \acrfull{wfs}~\cite{noauthor_schutzgebiete_nodate}.
	\section{Results}
	\section{Discussion}
	\section{Related Works}
	\section{Conclusion}

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{Web_Processing.bib}
